---
title: "CogLab Data Presentation"
subtitle: "Metacontrast Masking"
author: Jamie Daniels & Shannon McCarthy
date: February 14, 2019
output: slidy_presentation
---
Intro
===

- point 1
  - subpoint 
  
Background 
===

- Visual perception is a process that can be interupted or blocked by the introduction of a mask.
  - A mask is a brief stimuli that disrupts the perception of the target stimuli. 
  - 
- The purpose of this experiment is to have participants focus on the fixation point at the center of the screen and determine the position of the target stimuli (a retangle). 
- Three other squares will appear around the fixation point in addition to the rectangle 
- Each trial will have a box drawn around the four stimuli
- The time between the presentation of the stimuli and the box drawn will vary between trials
-Subjects indicate the location of the rectangle (top left, top right, bottom left, or bottom right)

Methods
===

**Variables of Interest**

Independent Variables      | Dependent Variable               | Constant
---------------------------|----------------------------------|-----------------
Stimulus onset asynchrony  | Proportion of correct resposes   | Fixation point 
Horizontal object position |                                  | 
Vertical object position   |                                  | 


**Participants**

- 77 undergraduate students ages (17-25)
- Males and Females 
- The students participated in this lab as part of the labratory in sensory processing class. 

Methods
===

**Equipment**

- Web Browser
- Computer or Tablet 
- LCD screen 
- Working internet connection
- keyboard/mouse (touchscreen capability if tablet)

Methods
===

**Procedures** 

- Participants look at the fixation point located at the middle of the screen
- Trails are self-initiated, press the "start next trial" button to begin a new trial, press the "redo trial" button redo a trial.
- In each 


Data Wrangling
===

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = FALSE)

```

Data Wrangling
===

```{r setup_rmd, echo=TRUE, warning=FALSE, message=FALSE}
library("tidyverse")
library("forcats")

data_file <-"mmask_all.csv"

data_set <- read_csv(ifelse(!file.exists(data_file),
                            paste("./CogLab_reports/coglab_pres/",
                                  data_file,sep="/"),data_file))

```

Data Wrangling 
===

```{r soa_count, echo=TRUE}

mask_acc<-data_set %>%
  group_by(randomGator,SOA) %>%
  count(Accuracy) %>%
  mutate(prop = prop.table(n)) # Filled in missing conmbinations of Accuracy, Target, SOA


```

Data Wrangling
===

```{r subj_avg_grp, echo=TRUE}

maska <- mask_acc %>%
  group_by(randomGator) %>%
  complete(Accuracy, SOA, fill = list(n = 0,prop = 0))

maska_grp <- maska %>% 
  group_by(Accuracy, SOA) %>% 
  summarise(sd=sd(prop),avg=mean(prop),ymin=avg-sd,ymax=avg+sd)


```

Results
===

```{r group_plot1, echo=TRUE, warning=FALSE}

ggplot(maska_grp %>% filter(Accuracy== 1),aes(x=SOA, y=avg, group= Accuracy)) +
  geom_line(size=2,color="royalblue") +
  geom_point(size = 3,color="royalblue") +
  geom_errorbar(aes(y=avg,ymin = ymin, ymax = ymax),width=0.7,color="royalblue")+
  scale_x_continuous(breaks = c(0,30,60,90,120,150,180))+
  scale_y_continuous("Proportion",breaks = c(-0.25,0.0,0.25,0.50,0.75,1.0)) + 
  theme_bw(24)+coord_cartesian(ylim=c(0,1))


```

 - Data from all subjects 

---

```{r echo=FALSE, warning=FALSE}



```


```{r echo=FALSE, fig.asp=0.3, fig.width=11}



```

Discussion of Results
=== 
